---
title: "Graphs shrimp genetics 2022"
#author: "Luigui Gallardo Becerra"
date: "07/12/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library("optparse")
library("ggplot2")
library("reshape")
require("gridExtra")
library("ggpubr")
library("ggh4x")
library("dplyr")
library("rstatix")
library("vegan")
library(tiff)
library(grid)
library("RColorBrewer")
library(VennDiagram)

```

## Supplementary figure 1: Rarefaction curves with all samples. A) Observed OTUs, B) Chao1 Index, C) Shannon Index and D) Good's Coverage

```{r , fig.align="center", echo=FALSE}
grid.raster(readTIFF("./05_final_figures/suppl_fig1.tiff"))
```

## Supplementary figure 2: Beta diversity contrasting Organs, Genetics and Ponds (Jaccard Index)
### Module A: Beta diversity contrasting Organs
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
data <- read.table(file ="./02_supplementary_figures/02_bdiv_jaccard/pcoa_data.txt",
    header = TRUE,
    sep = '\t')

group = data$Organ

# Define colors
colors <- c("mediumseagreen",
            "darkviolet")

# Define shapes
shapes <- c(15,
            16)

# Creation of plot
theme_set(theme_bw())
graph <- ggplot(data, aes(y = pc2.0.12926151779759.,
                          x = pc3.0.0821986422754955.)) +
geom_point(aes(col=group,
               shape=group),
           size = 3) +
stat_chull(aes(colour = group,
               fill = group),
          alpha = 0.1,
          geom = "polygon") +
scale_color_manual(values = colors) +
scale_shape_manual(values = shapes) +
  scale_fill_manual(values = colors) +
labs(x="PC3 (8.22%)", 
    y="PC2 (12.93%)",
    subtitle = "ANOSIM=0.3299; p-value=0.001",
    title = "") +
geom_hline(yintercept=0,
    color = "gray") +
geom_vline(xintercept=0,
    color = "gray") +
  theme(legend.title = element_blank(),
        legend.position = c(0.5, 1.1),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = -1))

graph

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig2_a.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

### Module B: Beta diversity contrasting Genetics
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
data <- read.table(file ="./02_supplementary_figures/02_bdiv_jaccard/pcoa_data.txt",
    header = TRUE,
    sep = '\t')

group = data$Genetic

# Define colors
colors <- c("royalblue",
            "orangered")

# Define shapes
shapes <- c(15, 16)

# Creation of plot
theme_set(theme_bw())
graph <- ggplot(data, aes(y = pc2.0.12926151779759.,
                          x = pc3.0.0821986422754955.)) +
geom_point(aes(col=group,
    shape=group),
    size = 3) +
stat_chull(aes(colour = group,
               fill = group),
          alpha = 0.1,
          geom = "polygon") +
scale_color_manual(values = colors) +
scale_shape_manual(values = shapes) +
  scale_fill_manual(values = colors) +
labs(x="PC3 (8.22%)", 
    y="PC2 (12.93%)",
    subtitle = "ANOSIM=0.1704; p-value=0.033",
    title = "") +
geom_hline(yintercept=0,
    color = "gray") +
geom_vline(xintercept=0,
    color = "gray") +
  theme(legend.title = element_blank(),
        legend.position = c(0.5, 1.1),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = -1))

graph

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig2_b.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

## Module C: Beta diversity contrasting Ponds
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
data <- read.table(file ="./02_supplementary_figures/02_bdiv_jaccard/pcoa_data.txt",
    header = TRUE,
    sep = '\t')

group = data$Pond

# Define colors
colors <- c( "royalblue",
             "darkgreen",
             "orangered")

# Define shapes
shapes <- c(15, 16, 17)

# Creation of plot
theme_set(theme_bw())
graph <- ggplot(data, aes(y = pc2.0.12926151779759.,
                          x = pc3.0.0821986422754955.)) +
geom_point(aes(col=group,
    shape=group),
    size = 3) +
stat_chull(aes(colour = group,
               fill = group),
          alpha = 0.1,
          geom = "polygon") +
scale_color_manual(values = colors) +
scale_shape_manual(values = shapes) +
  scale_fill_manual(values = colors) +
labs(x="PC3 (8.22%)", 
    y="PC2 (12.93%)",
    subtitle = "ANOSIM=0.1455; p-value=0.006",
    title = "") +
geom_hline(yintercept=0,
    color = "gray") +
geom_vline(xintercept=0,
    color = "gray") +
  theme(legend.title = element_blank(),
        legend.position = c(0.5, 1.1),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.text = element_text(size=11),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = -1))

graph

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig2_c.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

## Supplementary figure 3: Taxonomy (>0.01%) at 
### Module A phyla level
```{r, echo=FALSE, fig.width=6, fig.height=6}
# Input table
table <- read.table(file = "./01_main_figures/03_sumtax_0.01/phylum.txt",
                    header = TRUE,
                    sep = "\t")

# Colors
colourCount = length(unique(table$taxa))
getPalette = colorRampPalette(brewer.pal(9, "Set3"))

# Barplot
barplot_tax <- ggplot(table) +
geom_col(aes(x = pond,
    y = value,
    fill = taxa)) +
facet_grid(~organ) +
labs(x = "",
    y = "Relative abundance",
    fill = "Phyla") +
scale_x_discrete(expand = c(0, 0)) +
scale_y_continuous(limits = c(0, 1.01),
    expand = c(0, 0)) +
scale_fill_manual(values = getPalette(colourCount)) +
theme_test() +
theme(text = element_text(size = 15),
    axis.text.x = element_text(size = 14,
        angle = 45,
        hjust = 1),
    legend.title = element_text(size = 15,
    hjust = 0.5),
    legend.key.height = unit(1, "line"),
    legend.key.width = unit(1, "line")) +
guides(fill = guide_legend(ncol = 1, byrow = FALSE))

barplot_tax

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig3_a.tiff",
     width=6,
     height=6,
     dpi=300,
     device="tiff")
```

### Module B genera level clustered by organ and pond
```{r, echo=FALSE, fig.width=10, fig.height=7}
# Input table
table <- read.table(file = "./01_main_figures/03_sumtax_0.01/genus.txt",
                    header = TRUE,
                    sep = "\t")

# Colors
colourCount = length(unique(table$taxa))
getPalette = colorRampPalette(brewer.pal(9, "Set3"))

# Barplot
barplot_tax <- ggplot(table) +
geom_col(aes(x = pond,
    y = value,
    fill = taxa)) +
facet_grid(~organ) +
labs(x = "",
    y = "Relative abundance",
    fill = "Genera") +
scale_x_discrete(expand = c(0, 0)) +
scale_y_continuous(limits = c(0, 1.01),
    expand = c(0, 0)) +
scale_fill_manual(values = getPalette(colourCount)) +
theme_test() +
theme(text = element_text(size = 15),
    axis.text.x = element_text(size = 14,
        angle = 45,
        hjust = 1),
    legend.title = element_text(size = 15,
    hjust = 0.5),
    legend.key.height = unit(1, "line"),
    legend.key.width = unit(1, "line")) +
guides(fill = guide_legend(ncol = 3, byrow = FALSE))

barplot_tax

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig3_b.tiff",
     width=10,
     height=7,
     dpi=300,
     device="tiff")
```


## Supplementary figure 4: LEfSe of taxonomical classification contrasting gut and hepatopancreas samples
```{r, echo=FALSE, fig.width=7, fig.height=7}
# Data input
table <- read.table(file = "./02_supplementary_figures/04_lefse_tax_organs/organ_lefse_taxa.txt",
                    sep = "\t",
                    header = T)

# Define colors
colors <- c("darkviolet", "mediumseagreen")

# Barplot
barplot <- ggplot(data = table,
    aes(x = reorder(organ_taxa, -order),
    y = lda,
    fill = group)) +
geom_bar(stat = "identity") +
theme_test() +
scale_fill_manual(values = colors) +
labs(x = "",
    y = "LDA SCORE (log 10)",
    fill = "Associated\ngroup") +
theme(legend.position = "top") +
coord_flip(ylim = c(2, 5),
           expand = c(0, 0)) +
theme(text = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.text.y = element_text(size = 6),
    legend.title = element_text(size = 10,
        vjust = 1, hjust = 0.5))

barplot

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig4.tiff",
     width=7,
     height=7,
     dpi=300,
     device="tiff")
```

## Supplementary figure 5: LEfSe of PICRUSt predicted functions contrasting gut and hepatopancreas samples. KEGG level 3
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
table <- read.table(file = "./02_supplementary_figures/05_lefse_picrust_organs/organ_lefse_picrust_l3.txt",
                    sep = "\t",
                    header = T)

# Define colors
colors <- c("darkviolet", "mediumseagreen")

# Barplot
barplot <- ggplot(data = table,
    aes(x = reorder(organ_function, -order),
    y = lda,
    fill = group)) +
geom_bar(stat = "identity") +
theme_test() +
scale_fill_manual(values = colors) +
labs(x = "",
    y = "LDA SCORE (log 10)",
    fill = "Associated\ngroup") +
theme(legend.position = "top") +
coord_flip(ylim = c(1.99, 2.9),
           expand = c(0, 0)) +
theme(text = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.text.y = element_text(size = 6),
    legend.title = element_text(size = 10,
        vjust = 1, hjust = 0.5))

barplot

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig5.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

## Supplementary figure 6: LEfSe of PICRUSt predicted functions contrasting gut samples between genetics. A) KEGG level 2 and B) KEGG level 3.


## Supplementary figure 7: Venn diagrams of shared OTUs contrasting genetics. A) Intestine samples and B) hepatopancreas samples
```{r , fig.align="center", echo=FALSE}
grid.raster(readTIFF("./05_final_figures/suppl_fig7.tiff"))
```


## Supplementary figure 8: Alpha diversity and niche breadth contrasting genetics between intestine samples
### Module A Chao1
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
alpha_data <- read.table(file = "./01_main_figures/07_adiv_niche_breadht_gut/gut_all_metrics.txt",
                         sep = "\t",
                         header = T)

# Define colors
colors <- c("royalblue", "orangered")
p_value <- list(c("Genetic 1", "Genetic 2"))

### chao1
boxplot <- ggplot(alpha_data, aes(x = group, y = chao1)) +
geom_boxplot(aes(color = group),
    outlier.shape = NA) +
geom_point(aes(color = group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Chao1 Index") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
                   method = "wilcox.test") +
theme(text = element_text(size=12),
      axis.title.y = element_text(size=12))

boxplot

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig8_a.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

### Module B Shannon
```{r, echo=FALSE, fig.width=5, fig.height=5}
### Shannon ###
boxplot <- ggplot(alpha_data, aes(x = group, y = shannon)) +
geom_boxplot(aes(color = group),
    outlier.shape = NA) +
geom_point(aes(color = group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Shannon Index") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
                   method = "wilcox.test") +
theme(text = element_text(size=12),
      axis.title.y = element_text(size=12))

boxplot

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig8_b.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```


### Module C niche breadth
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
table <- read.delim(file = "./01_main_figures/07_adiv_niche_breadht_gut/values_niche_widht_otu_table_s_0.01_gut_genetics.txt",
    header = TRUE)

# Define colors and variables
colors <- c("royalblue", "orangered")
p_value <- list(c("Genetic 1", "Genetic 2"))

# Plot
barplot_niche <- ggplot(table,
    aes(x = group,
        y = value),
        fill = group) +
geom_boxplot(aes(color = group),
    outlier.shape = NA) +
geom_point(aes(color = group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Niche breadth") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
                   method = "wilcox.test") +
theme(text = element_text(size=12),
      axis.title.y = element_text(size=12))

barplot_niche

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig8_c.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

### Supplementary figure 9: Alpha diversity and niche breadth contrasting genetics between hepatopancreas samples; A) Chao1 and B) Shannon and C) niche breadth.
### Module A Chao1
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
alpha_data <- read.table(file = "./01_main_figures/08_adiv_niche_breadht_hep/hep_all_metrics.txt",
                         sep = "\t",
                         header = T)

# Define colors
colors <- c("royalblue", "orangered")
p_value <- list(c("Genetic 1", "Genetic 2"))

### chao1
boxplot <- ggplot(alpha_data, aes(x = group, y = chao1)) +
geom_boxplot(aes(color = group),
    outlier.shape = NA) +
geom_point(aes(color = group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Chao1 Index") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
                   method = "wilcox.test") +
theme(text = element_text(size=12),
      axis.title.y = element_text(size=12))

boxplot

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig9_a.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

### Module B Shannon
```{r, echo=FALSE, fig.width=5, fig.height=5}
### Shannon ###
boxplot <- ggplot(alpha_data, aes(x = group, y = shannon)) +
geom_boxplot(aes(color = group),
    outlier.shape = NA) +
geom_point(aes(color = group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Shannon Index") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
                   method = "wilcox.test") +
theme(text = element_text(size=12),
      axis.title.y = element_text(size=12))

boxplot

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig9_b.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

### Module C niche breadth
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
table <- read.delim(file = "./01_main_figures/08_adiv_niche_breadht_hep/values_niche_widht_otu_table_s_0.01_hep_genetics.txt",
    header = TRUE)

# Define colors and variables
colors <- c("royalblue", "orangered")
p_value <- list(c("Genetic 1", "Genetic 2"))

# Plot
barplot_niche <- ggplot(table,
    aes(x = group,
        y = value),
        fill = group) +
geom_boxplot(aes(color = group),
    outlier.shape = NA) +
geom_point(aes(color = group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Niche breadth") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
                   method = "wilcox.test") +
theme(text = element_text(size=12),
      axis.title.y = element_text(size=12))

barplot_niche

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig9_c.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```


## Supplementary figure 10: Probiotics constrasting between organs and genetics
### Module A: Barplots with probiotics genera-level
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Barplot probiotics, only intestine samples
probiotics_gut_genera <- data.frame(
  group=c("Intestine\nGenetic 1",
         "Intestine\nGenetic 2",
         "Hepatopancreas\nGenetic 1",
         "Hepatopancreas\nGenetic 2"),
  value=c(0.373722,
          0.320628,
          0.344285,
          0.290699)
  )

# Define colors
colors <- c("darkviolet", "mediumseagreen",
            "darkviolet", "mediumseagreen")

# Heatmap
barplot <- ggplot(data = probiotics_gut_genera,
    aes(x = value,
    y = group,
    fill = group)) +
geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_manual(values = colors) +
theme_test() +
  scale_x_continuous(limits = c(0, 0.45),
                     expand = c(0, 0)) +
labs(x = "Relative abundance",
    y = "",
    title = "Genera-level probiotics") +
theme(legend.position = "none",
      text = element_text(size=12),
      axis.title.y = element_text(size=12),
      plot.title = element_text(hjust = 0.5))

barplot

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig10_a.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

### Module B: Barplots with probiotics species-level
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Barplot probiotics, only intestine samples
probiotics_gut_species <- data.frame(
  group=c("Intestine\nGenetic 1",
         "Intestine\nGenetic 2",
         "Hepatopancreas\nGenetic 1",
         "Hepatopancreas\nGenetic 2"),
  value=c(0.002824,
          0.001605,
          0.007651,
          0.001657)
  )

# Define colors
colors <- c("darkviolet", "mediumseagreen",
            "darkviolet", "mediumseagreen")

# Heatmap
barplot <- ggplot(data = probiotics_gut_species,
    aes(x = value,
    y = group,
    fill = group)) +
geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_manual(values = colors) +
theme_test() +
  scale_x_continuous(limits = c(0, 0.008),
                     expand = c(0, 0)) +
labs(x = "Relative abundance",
     y = "",
     title = "Species-level probiotics") +
theme(legend.position = "none",
      text = element_text(size=12),
      axis.title.y = element_text(size=12),
      plot.title = element_text(hjust = 0.5))

barplot

#Plot tiff
ggsave(filename = "./05_final_figures/suppl_fig10_b.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

## Supplementary figure 11: Beta diversity contrasting Ponds A and B (Unweighted UniFrac)
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
data <- read.table(file ="01_main_figures/02_bdiv_unweighted_unifrac/pcoa_data_Maz_Est.txt",
    header = TRUE,
    sep = '\t')

group = data$Pond

# Define colors
colors <- c( "royalblue",
             "darkgreen")

# Define shapes
shapes <- c(15, 16)

# Creation of plot
theme_set(theme_bw())
graph <- ggplot(data, aes(y = pc1.0.297501699.,
                          x = pc2.0.174429323799868.)) +
geom_point(aes(col=group,
    shape=group),
    size = 3) +
stat_chull(aes(colour = group,
               fill = group),
          alpha = 0.1,
          geom = "polygon") +
scale_color_manual(values = colors) +
scale_shape_manual(values = shapes) +
  scale_fill_manual(values = colors) +
labs(x="PC1 (29.75%)", 
    y="PC2 (17.44%)",
    subtitle = "ANOSIM=0.074; p-value=0.084",
    title = "") +
geom_hline(yintercept=0,
    color = "gray") +
geom_vline(xintercept=0,
    color = "gray") +
  theme(legend.title = element_blank(),
        legend.position = c(0.5, 1.1),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.text = element_text(size=11),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = -1))

graph

#Plot tiff
ggsave(filename = "05_final_figures/suppl_fig11.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

## Supplementary figure 12: Beta diversity contrasting Ponds A and B (Jaccard)
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
data <- read.table(file ="02_supplementary_figures/02_bdiv_jaccard/pcoa_data_Maz_Est.txt",
    header = TRUE,
    sep = '\t')

group = data$Pond

# Define colors
colors <- c( "royalblue",
             "darkgreen")

# Define shapes
shapes <- c(15, 16)

# Creation of plot
theme_set(theme_bw())
graph <- ggplot(data, aes(y = pc1.0.253863540954829.,
                          x = pc2.0.13696005199046.)) +
geom_point(aes(col=group,
    shape=group),
    size = 3) +
stat_chull(aes(colour = group,
               fill = group),
          alpha = 0.1,
          geom = "polygon") +
scale_color_manual(values = colors) +
scale_shape_manual(values = shapes) +
  scale_fill_manual(values = colors) +
labs(x="PC1 (29.75%)", 
    y="PC2 (17.44%)",
    subtitle = "ANOSIM=0.1069; p-value=0.044",
    title = "") +
geom_hline(yintercept=0,
    color = "gray") +
geom_vline(xintercept=0,
    color = "gray") +
  theme(legend.title = element_blank(),
        legend.position = c(0.5, 1.1),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.text = element_text(size=11),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = -1))

graph

#Plot tiff
ggsave(filename = "05_final_figures/suppl_fig12.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```