---
title: "Graphs shrimp genetics 2022"
#author: "Luigui Gallardo Becerra"
date: "07/12/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library("optparse")
library("ggplot2")
library("reshape")
require("gridExtra")
library("ggpubr")
library("ggh4x")
library("dplyr")
library("rstatix")
library("vegan")
```

## Figure 1: Beta diversity contrasting Organs, Genetics and Ponds
### Module A: Beta diversity contrasting Organs
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
data <- read.table(file ="01_main_figures/02_bdiv_unweighted_unifrac/pcoa_data.txt",
    header = TRUE,
    sep = '\t')

group = data$Organ

# Define colors
colors <- c("mediumseagreen",
            "darkviolet")

# Define shapes
shapes <- c(15,
            16)

# Creation of plot
theme_set(theme_bw())
graph <- ggplot(data, aes(y = pc2.0.18351911740638438.,
                          x = pc3.0.07089508464704075.)) +
geom_point(aes(col=group,
               shape=group),
           size = 3) +
stat_chull(aes(colour = group,
               fill = group),
          alpha = 0.1,
          geom = "polygon") +
scale_color_manual(values = colors) +
scale_shape_manual(values = shapes) +
  scale_fill_manual(values = colors) +
labs(x="PC3 (7.09%)", 
    y="PC2 (18.35%)",
    subtitle = "ANOSIM=0.3391; p-value=0.001",
    title = "") +
geom_hline(yintercept=0,
    color = "gray") +
geom_vline(xintercept=0,
    color = "gray") +
  theme(legend.title = element_blank(),
        legend.position = c(0.5, 1.1),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = -1))
        

graph

#Plot tiff
ggsave(filename = "05_final_figures/fig1_a.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

### Module B: Beta diversity contrasting Genetics
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
data <- read.table(file ="01_main_figures/02_bdiv_unweighted_unifrac/pcoa_data.txt",
    header = TRUE,
    sep = '\t')

group = data$Genetic

# Define colors
colors <- c("royalblue",
            "orangered")

# Define shapes
shapes <- c(15, 16)

# Creation of plot
theme_set(theme_bw())
graph <- ggplot(data, aes(y = pc2.0.18351911740638438.,
                          x = pc3.0.07089508464704075.)) +
geom_point(aes(col=group,
    shape=group),
    size = 3) +
stat_chull(aes(colour = group,
               fill = group),
          alpha = 0.1,
          geom = "polygon") +
scale_color_manual(values = colors) +
scale_shape_manual(values = shapes) +
  scale_fill_manual(values = colors) +
labs(x="PC3 (7.09%)", 
    y="PC2 (18.35%)",
    subtitle = "ANOSIM=0.1729; p-value=0.023",
    title = "") +
geom_hline(yintercept=0,
    color = "gray") +
geom_vline(xintercept=0,
    color = "gray") +
  theme(legend.title = element_blank(),
        legend.position = c(0.5, 1.1),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = -1))

graph

#Plot tiff
ggsave(filename = "05_final_figures/fig1_b.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

## Module C: Beta diversity contrasting Ponds
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
data <- read.table(file ="01_main_figures/02_bdiv_unweighted_unifrac/pcoa_data.txt",
    header = TRUE,
    sep = '\t')

group = data$Pond

# Define colors
colors <- c( "royalblue",
             "darkgreen",
             "orangered")

# Define shapes
shapes <- c(15, 16, 17)

# Creation of plot
theme_set(theme_bw())
graph <- ggplot(data, aes(y = pc2.0.18351911740638438.,
                          x = pc3.0.07089508464704075.)) +
geom_point(aes(col=group,
    shape=group),
    size = 3) +
stat_chull(aes(colour = group,
               fill = group),
          alpha = 0.1,
          geom = "polygon") +
scale_color_manual(values = colors) +
scale_shape_manual(values = shapes) +
  scale_fill_manual(values = colors) +
labs(x="PC3 (7.09%)", 
    y="PC2 (18.35%)",
    subtitle = "ANOSIM=0.1185; p-value=0.006",
    title = "") +
geom_hline(yintercept=0,
    color = "gray") +
geom_vline(xintercept=0,
    color = "gray") +
  theme(legend.title = element_blank(),
        legend.position = c(0.5, 1.1),
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.text = element_text(size=11),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = -1))

graph

#Plot tiff
ggsave(filename = "05_final_figures/fig1_c.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```

## Figure 2: Alpha Diversity
### Module A and B: Alpha diversity contrasting Organs, Chao1 and Shannon
```{r, echo=FALSE, fig.width=5, fig.height=5}
alpha_data <- read.table(file = "01_main_figures/04_adiv_organs/alpha_organ.txt",
                         sep = "\t",
                         header = T)
# Define colors
colors <- c("darkviolet",
            "mediumseagreen")

# Groups to compare
p_value <- list(c("Intestine",
                  "Hepatopancreas"))

# Chao1
chao1_boxplot <- ggplot(alpha_data,
                  aes(x = group,
                      y = chao1)) +
geom_boxplot(aes(color = group),
             outlier.shape = NA) +
geom_point(aes(color = group),
           size = 2,
           shape = 21,
           position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
     y = "Chao1 Index") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
                   method = "wilcox.test") +
theme(text = element_text(size=12),
      axis.title.y = element_text(size=12))

chao1_boxplot

#Plot tiff
ggsave(filename = "05_final_figures/fig2_a.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")
```


```{r, echo=FALSE, fig.width=5, fig.height=5}
# Shannon
shannon_boxplot <- ggplot(alpha_data,
                  aes(x = group,
                      y = shannon)) +
geom_boxplot(aes(color = group),
    outlier.shape = NA) +
geom_point(aes(color = group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Shannon Index") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
    method = "wilcox.test") +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12))

shannon_boxplot

#Plot tiff
ggsave(filename = "05_final_figures/fig2_b.tiff",
       width=5,
       height=5,
       dpi=300,
       device="tiff")
```

### Module C: Distance to centroid contrasting Organs
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
table <- as.dist(read.table(file = "01_main_figures/06_niche_breadht_centroid_organs/unweighted_unifrac_dm_all-samples.txt",
    header = 1, 
    row.names = 1,
    sep = "\t"))
# Define colors and variables
name <- (labels = c("HL7", "HE8", "HL5", "HL4", "HL2", "HL1", "HE4", "HE5", 
                    "HE7", "HE1", "HE2", "IE3", "IE2", "IE5", "IE7", "HA8", 
                    "IA9", "IA8", "IA5", "HA1", "IA7", "HA5", "IA3", "IA2", 
                    "IE9", "IE8", "IA4", "HA2", "IL6", "IL4", "IL2", "IL3", 
                    "IL1", "HA7", "IL8"))
organ <- (labels = c("Hepatopancreas", "Hepatopancreas", "Hepatopancreas", "Hepatopancreas", 
                     "Hepatopancreas", "Hepatopancreas", "Hepatopancreas", "Hepatopancreas", 
                     "Hepatopancreas", "Hepatopancreas", "Hepatopancreas", "Intestine", "Intestine", "Intestine", 
                     "Intestine", "Hepatopancreas", "Intestine", "Intestine", "Intestine", "Hepatopancreas", "Intestine", "Hepatopancreas", 
                     "Intestine", "Intestine", "Intestine", "Intestine", "Intestine", "Hepatopancreas", "Intestine", "Intestine", "Intestine", "Intestine", "Intestine", 
                     "Hepatopancreas", "Intestine"))


# Define colors
colors <- c("darkviolet", "mediumseagreen")

# Groups to compare
p_value <- list(c("Intestine", "Hepatopancreas"))

# Betadisper
organ_bdisp <- betadisper(table,
    organ,
    type = c("median"))

organ_df <- data.frame(Distance_to_centroid=organ_bdisp$distances,
    Group = organ_bdisp$group)

# Boxplot
boxplot_dist_centroid <- ggplot(organ_df,
    aes(x = Group,
    y = Distance_to_centroid)) +
geom_boxplot(aes(color = Group),
    outlier.shape = NA) +
geom_point(aes(color = Group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Distance to centroid") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
    method = "wilcox.test") +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12))

boxplot_dist_centroid

#Plot tiff
ggsave(filename = "05_final_figures/fig2_c.tiff",
       width=5,
       height=5,
       dpi=300,
       device="tiff")

```

### Module D and E: Alpha diversity contrasting Genetics (Mazatlan and Lajitas only), Chao1 and Shannon
```{r, echo=FALSE, fig.width=5, fig.height=5}
alpha_data <- read.table(file = "01_main_figures/11_adiv_genetics/genetics_alpha.txt",
                         sep = "\t",
                         header = T)
# Define colors
colors <- c("royalblue",
            "orangered")

# Groups to compare
  p_value <- list(c("Genetic 1 (Gen1)",
                  "Genetic 2 (Gen2)"))
# Chao1
chao1_boxplot <- ggplot(alpha_data,
                  aes(x = group,
                      y = chao1)) +
geom_boxplot(aes(color = group),
             outlier.shape = NA) +
geom_point(aes(color = group),
           size = 2,
           shape = 21,
           position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
     y = "Chao1 Index") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
                   method = "wilcox.test") +
theme(text = element_text(size=12),
      axis.title.y = element_text(size=12))

chao1_boxplot

#Plot tiff
ggsave(filename = "05_final_figures/fig2_d.tiff",
     width=5,
     height=5,
     dpi=300,
     device="tiff")

```

```{r, echo=FALSE, fig.width=5, fig.height=5}
# Shannon
shannon_boxplot <- ggplot(alpha_data,
                  aes(x = group,
                      y = shannon)) +
geom_boxplot(aes(color = group),
    outlier.shape = NA) +
geom_point(aes(color = group),
    size = 2,
    shape = 21,
    position = position_jitterdodge()) +
theme_test() +
theme(legend.position = "none") +
labs(x = "",
    y = "Shannon Index") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
    method = "wilcox.test") +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12))

shannon_boxplot

#Plot tiff
ggsave(filename = "05_final_figures/fig2_e.tiff",
       width=5,
       height=5,
       dpi=300,
       device="tiff")
```

### Module F: Niche breadth contrasting Genetics (Mazatlan and Lajitas only)
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Niche breadth
# Data input
table <- read.table(file = "01_main_figures/05_niche_breadht_genetics/values_niche_widht_otu_table_s_0.01_genetics.txt",
    header = TRUE,
    sep = "\t")

# Define colors and variables
colors <- c("royalblue",
            "orangered")

p_value <- list(c("Genetic 1",
                  "Genetic 2"))
# Plot
boxplot_niche <- ggplot(table,
                        aes(x = group,
                            y = value),
                        fill = group) +
  geom_boxplot(aes(color = group),
               outlier.shape = NA) +
  geom_point(aes(color = group),
             size = 2,
             shape = 21,
             position = position_jitterdodge()) +
  theme_test() +
  theme(legend.position = "none") +
  labs(x = "",
       y = "Niche breadth") +
scale_color_manual(values = colors) +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12)) +
stat_compare_means(comparisons = p_value,
    method = "wilcox.test") +
theme(text = element_text(size=12),
    axis.title.y = element_text(size=12))

boxplot_niche
#Plot tiff
ggsave(filename = "05_final_figures/fig2_g.tiff",
       width=5,
       height=5,
       dpi=300,
       device="tiff")
```

## Figure 3: LEfSe heatmaps and barplots
### Module A: Intestine samples contrasting genetics
```{r, echo=FALSE, fig.width=6, fig.height=6}
# Data input
table <- read.table(file = "01_main_figures/09_lefse_tax_gut/gut_lefse_taxa.txt",
    sep = "\t", header = T,
    check.names = FALSE)

table_heatmap <- read.table(file = "01_main_figures/09_lefse_tax_gut/gut_lefse_taxa_heatmap_samples.txt",
    sep = "\t", header = T,
    check.names = FALSE)

# Define colors
colors <- c("royalblue", "orangered")

# Heatmap
heatmap <- ggplot(data = table_heatmap,
    aes(x = reorder(variable, -order),
    y = sample,
    fill = value)) +
geom_tile() +
theme_test() +
coord_flip() +
scale_fill_distiller(palette = "YlOrRd",
    direction = 1) +
facet_grid(~group,
    scales = "free") +
theme(legend.position = "top") +
labs(x = "",
    y = "",
    fill = "log10 (relative\nabundance)",
    title = "Intestine") +
theme(text = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.text.y = element_text(size = 7,
        vjust = 0.25),
    axis.text.x = element_text(angle = 90,
                               vjust = 0.5),
    legend.title = element_text(size = 10,
        vjust = 1, hjust = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.text = element_text(size = 6),
    plot.margin=unit(c(0.1,0.5,0.5,0.5), "cm"))

# Barplot
barplot <- ggplot(data = table,
    aes(x = reorder(gut_taxa, -order),
    y = lda,
    fill = group)) +
geom_bar(stat = "identity") +
theme_test() +
coord_flip(ylim = c(2, 5),
           expand = TRUE) +
scale_fill_manual(values = colors) +
labs(x = "",
    y = "LDA SCORE (log10)",
    fill = "") +
theme(legend.position = "top") +
theme(text = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.text.y = element_blank(),
    legend.title = element_text(size = 10,
        vjust = 1, hjust = 0.5),
    axis.ticks.y = element_blank(),
    plot.margin=unit(c(1.76,0.5,0.71,-1.1), "cm"))

# Complete module
ggarrange(heatmap,
          barplot + rremove("y.text"),
          ncol = 2,
          nrow = 1,
          widths = c(2, 1))

#Plot tiff
ggsave(filename = "05_final_figures/fig3_a.tiff",
       width=5,
       height=5,
       dpi=300,
       device="tiff")
```


### Module B: Hepatopancreas samples contrasting genetics
```{r, echo=FALSE, fig.width=6, fig.height=6}
# Data input
table <- read.table(file = "01_main_figures/10_lefse_tax_hep/hep_lefse_taxa.txt",
    sep = "\t", header = T,
    check.names = FALSE)

table_heatmap <- read.table(file = "01_main_figures/10_lefse_tax_hep/hep_lefse_taxa_heatmap_samples.txt",
    sep = "\t", header = T,
    check.names = FALSE)

# Define colors
colors <- c("royalblue", "orangered")

# Heatmap
heatmap <- ggplot(data = table_heatmap,
    aes(x = reorder(variable, -order),
    y = sample,
    fill = value)) +
geom_tile() +
theme_test() +
coord_flip() +
scale_fill_distiller(palette = "YlOrRd",
    direction = 1) +
facet_grid(~group,
    scales = "free") +
theme(legend.position = "top") +
labs(x = "",
    y = "",
    fill = "log10 (relative\nabundance)",
    title = "Hepatopancreas") +
theme(text = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.text.y = element_text(size = 7,
        vjust = 0.25),
    axis.text.x = element_text(angle = 90,
                               vjust = 0.5),
    legend.title = element_text(size = 10,
        vjust = 1, hjust = 0.5),
    plot.title = element_text(hjust = 0.5),
    legend.text = element_text(size = 6),
    plot.margin=unit(c(0.1,0.5,0.5,0.5), "cm"))

# Barplot
barplot <- ggplot(data = table,
    aes(x = reorder(hep_taxa, -order),
    y = lda,
    fill = group)) +
geom_bar(stat = "identity") +
theme_test() +
coord_flip(ylim = c(2, 5),
           expand = TRUE) +
scale_fill_manual(values = colors) +
labs(x = "",
    y = "LDA SCORE (log10)",
    fill = "") +
theme(legend.position = "top") +
theme(text = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.text.y = element_blank(),
    legend.title = element_text(size = 10,
        vjust = 1, hjust = 0.5),
    axis.ticks.y = element_blank(),
    plot.margin=unit(c(1.77,0.5,0.87,-1.1), "cm"))

# Complete module
ggarrange(heatmap,
          barplot + rremove("y.text"),
          ncol = 2,
          nrow = 1,
          widths = c(2, 1))

#Plot tiff
ggsave(filename = "05_final_figures/fig3_b.tiff",
       width=5,
       height=5,
       dpi=300,
       device="tiff")
```

## Figure 4: Heatmap probiotics
### Module A: Intestine samples
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Data input
table <- read.table(file = "03_probiotics/allsamples_probiotics_heatmap_log10.txt",
    sep = "\t",
    header = T,
    check.names = FALSE)

table <- melt(table, id=c("sample","group"))

table$group <- factor(table$group, levels = c("Hepatopancreas Gen1", "Hepatopancreas Gen2",
    "Intestine Gen1", "Intestine Gen2",
    "Intestine healthy", "Intestine diseased"))

# Only Hepatopancreascreas
table_hep <- filter(table, group == "Hepatopancreas Gen1" | group == "Hepatopancreas Gen2")

# Heatmap
heatmap_prob <- ggplot(data = table_hep,
    aes(x = sample,
    y = variable,
    fill = value)) +
geom_tile() +
theme_test() +
scale_y_discrete(limits = rev(levels(table_hep$variable))) +
scale_fill_distiller(palette = "YlOrRd",
    direction = 1) +
theme(legend.position = "top") +
labs(x = "",
    y = "",
    fill = "log10 (relative\nabundance)") +
facet_grid(~group,
    scales = "free") +
theme(axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 7,
        vjust = 0.25),
    legend.title = element_text(size = 10,
        vjust = 1, hjust = 0.5),
    legend.text = element_text(size = 6),
    strip.text.x = element_text(size = 8))

heatmap_prob

#Plot tiff
ggsave(filename = "05_final_figures/fig4_a.tiff",
       width=5,
       height=5,
       dpi=300,
       device="tiff")

```

### Module A: Hepatopancreas samples

```{r, echo=FALSE, fig.width=5, fig.height=5}
# Only hepatopancreas
table_hep <- filter(table, group == "Intestine Gen1" | group == "Intestine Gen2")

# Heatmap
heatmap_prob <- ggplot(data = table_hep,
    aes(x = sample,
    y = variable,
    fill = value)) +
geom_tile() +
theme_test() +
scale_y_discrete(limits = rev(levels(table_hep$variable))) +
scale_fill_distiller(palette = "YlOrRd",
    direction = 1) +
theme(legend.position = "top") +
labs(x = "",
    y = "",
    fill = "log10 (relative\nabundance)") +
facet_grid(~group,
    scales = "free") +
theme(axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 7,
        vjust = 0.25),
    legend.title = element_text(size = 10,
        vjust = 1, hjust = 0.5),
    legend.text = element_text(size = 6),
    strip.text.x = element_text(size = 8))

heatmap_prob

#Plot tiff
ggsave(filename = "05_final_figures/fig4_b.tiff",
       width=5,
       height=5,
       dpi=300,
       device="tiff")
```

