---
title: "boxplots_probiotics_genetics"
output: pdf_document
date: "2024-09-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library("optparse")
library("ggplot2")
library("reshape")
require("gridExtra")
library("ggpubr")
library("ggh4x")
library("dplyr")
library("rstatix")
library("vegan")
```

## Boxplots probiotics gut
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Boxplot function definition
generate_probiotics_boxplot <- function(data_file, comparison, groups_to_compare, colors, y_axis, output_file) {
  # Load necessary libraries
  library("ggplot2")
  library("ggpubr")
  library("dplyr")
  
  # Read the data
  data <- read.table(file = data_file, sep = "\t", header = TRUE)
  
  data$group <- factor(data$group, levels = unique(data$group))
  
  # Define colors
  colors <- colors
  
  # Create the boxplot
  probiotics_boxplot <- ggplot(data, aes(x = group, y = !!sym(comparison))) +
    geom_boxplot(aes(color = group), outlier.shape = NA) +
    geom_point(aes(color = group), size = 2, shape = 21, position = position_jitterdodge()) +
    theme_test() +
    theme(legend.position = "none") +
    labs(x = "", y = y_axis) +
    scale_color_manual(values = colors) +
    theme(text = element_text(size = 12), axis.title.y = element_text(size = 12)) +
    stat_compare_means(comparisons = groups_to_compare, method = "wilcox.test", digits=4)
  
  # Save the plot as pdf
  ggsave(paste0(output_file, ".pdf"), plot = probiotics_boxplot, width = 5, height = 5, units = "in")
  
  # Save the plot as TIFF
  ggsave(paste0(output_file, ".tiff"), plot = probiotics_boxplot, width = 5, height = 5, units = "in", dpi = 300)

  # Show the plot
  probiotics_boxplot
}
```

## Metacomunity Gut & Hepatopancreas
### Metacommunity Gut & Hepatopancreas Observed OTUs
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_both_organs.tsv", 
                            comparison = "observed_otus_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Observed",
                            output_file = "./organs_observed_otus_allprobiotics")
```

### Metacommunity Gut & Hepatopancreas Chao1
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_both_organs.tsv", 
                            comparison = "chao1_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Chao1",
                            output_file = "./organs_chao1_allprobiotics")
```

### Metacommunity Gut & Hepatopancreas Shannon
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_both_organs.tsv", 
                            comparison = "shannon_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Shannon",
                            output_file = "./organs_shannon_allprobiotics")
```

## Metacommunity Gut
### Metacommunity Gut Observed OTUs
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_gut.tsv", 
                            comparison = "observed_otus_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Observed",
                            output_file = "./gut_observed_otus_allprobiotics")
```

### Metacommunity Gut Chao1
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_gut.tsv", 
                            comparison = "chao1_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Chao1",
                            output_file = "./gut_chao1_allprobiotics")
```

### Metacommunity Gut Shannon
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_gut.tsv", 
                            comparison = "shannon_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Shannon",
                            output_file = "./gut_shannon_allprobiotics")
```

## Metacommunity Hepatopancreas
### Metacommunity Hepatopancreas Observed OTUs
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_hep.tsv", 
                            comparison = "observed_otus_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Observed",
                            output_file = "./hep_observed_otus_allprobiotics")
```

### Metacommunity Hepatopancreas Chao1
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_hep.tsv", 
                            comparison = "chao1_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Chao1",
                            output_file = "./hep_chao1_allprobiotics")
```

### Metacommunity Hepatopancreas Shannon
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_hep.tsv", 
                            comparison = "shannon_allprobiotics",
                            groups_to_compare = list(c("Gen1", "Gen2")),
                            colors = c("royalblue", "orangered"),
                            y_axis = "Shannon",
                            output_file = "./hep_shannon_allprobiotics")
```

## Metacommunity Healthy vs Diseased
### Metacommunity Healthy vs Diseased Observed OTUs
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_ems.tsv", 
                            comparison = "observed_otus_allprobiotics",
                            groups_to_compare = list(c("Healthy", "Disease")),
                            colors <- c("darkviolet", "mediumseagreen"),
                            y_axis = "Observed",
                            output_file = "./ems_observed_otus_allprobiotics")
```

### Metacommunity Healthy vs Diseased Chao1
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_ems.tsv", 
                            comparison = "chao1_allprobiotics",
                            groups_to_compare = list(c("Healthy", "Disease")),
                            colors <- c("darkviolet", "mediumseagreen"),
                            y_axis = "Chao1",
                            output_file = "./ems_chao1_allprobiotics")
```

### Metacommunity Healthy vs Diseased Shannon
```{r, echo=FALSE, fig.width=5, fig.height=5}
# Gut probiotics genus
generate_probiotics_boxplot(data_file = "./adiv_metrics_ems.tsv", 
                            comparison = "shannon_allprobiotics",
                            groups_to_compare = list(c("Healthy", "Disease")),
                            colors <- c("darkviolet", "mediumseagreen"),
                            y_axis = "Shannon",
                            output_file = ".ems_shannon_allprobiotics")
```
